\LARGE \bf Predicting Initialization Effectiveness for Trajectory Optimization

### 2014-02-07 paper.tex
Added text descriptions of new features.

>>>>

\subsection{Feature IV: Convexity Features}
	Another category of features used measured the local convexity of the problem around the trajectory. Since trajopt takes local convex approximations around the trajectory at each iteration in the 'convexify' step, these features measure how close the approximations are.

	We computed eigenvalues of Hessian matrices of cost and constraint functions at the trajectory. We computed the following features on the eigenvalues to measure their negativity i.e. the problem's local nonconvexity: $i.$ The minimum eigenvalue. $ii.$ The sum of negative eigenvalues. $iii.$ The maximum eigenvalue. $iv.$ The sum of all eigenvalues. We computed these 4 statistics for each cost and constraint function individually, and for all of them combined (e.g. the sum of all eigenvalues of all Hessian matrices), for a total of $4 \times [(number\ of\ cost\ functions) + (number\ of\ constraint\ functions) + 1)]$ convexity features. We collected the features in a feature vector denoted ${\bf z}_\textrm{conv}$.
